---
title: "Siemens_report"
author: "Siming Yan"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    # css: bootstrap.min.css
    theme: yeti
---

<style>
.colored {
  background-color: #FAFAFA;
}
</style>



``` {js}
// Inverse color of navigation bar.
$('.navbar-inverse').removeClass('navbar-inverse').addClass('navbar-default');
```

```{r setup, include = FALSE}
 
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)

```

```{r setup2, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(reshape2)
library(lubridate)
library(highcharter) # Interactive data visualizations
library(viridis)
library(DT)
library(lfe)
library(stargazer)
library(tidyverse)
library(stringr)
library(lubridate)
library(zoo)
library(forecast)
library(Hmisc) 
library(xts)
library(reticulate)
library(plotly)
# reticulate::use_condaenv("siming")
# vignette("highcharter")
# vignette("highcharts-api")
```


```{r, include=FALSE}
# Create a custom theme for the plots. 
custom_theme <- hc_theme(
  colors = c('#5CACEE', '#ee9e5c','#eee75c', '#5ceee7'),
  chart = list(
         backgroundColor = '#FAFAFA', 
         plotBorderColor = "black"),
  xAxis = list(
         gridLineColor = "E5E5E5", 
         labels = list(style = list(color = "#333333")), 
         lineColor = "#E5E5E5", 
         minorGridLineColor = "#E5E5E5", 
         tickColor = "#E5E5E5", 
         title = list(style = list(color = "#333333"))), 
  yAxis = list(
         gridLineColor = "#E5E5E5", 
         labels = list(style = list(color = "#333333")), 
         lineColor = "#E5E5E5", 
         minorGridLineColor = "#E5E5E5", 
         tickColor = "#E5E5E5", 
         tickWidth = 1, 
         title = list(style = list(color = "#333333"))),   
  title = list(style = list(color = '#333333', fontFamily = "Lato")),
  subtitle = list(style = list(color = '#666666', fontFamily = "Lato")),
  legend = list(
         itemStyle = list(color = "#333333"), 
         itemHoverStyle = list(color = "#FFF"), 
         itemHiddenStyle = list(color = "#606063")), 
  credits = list(style = list(color = "#666")),
  itemHoverStyle = list(color = 'gray'))
kbt <- function(...){
  knitr::kable(..., format.args = list(big.mark = ',', scientific = F)) %>%
    kableExtra::kable_styling(c("striped", "condensed"),
                               full_width = F,
                               position = "center",
                               row_label_position = "c") %>%
   row_spec(0, bold = T)
}

stg <- function(...){
  stargazer::stargazer(..., 
          type = "text",
          # style = "qje",
          # title = "daily_kwh ~ post:encouraged|customer_id + no.bill|0|customer_id",
          keep.stat = c("n", "ser"),
          digits = 5)
}

parent_cat1 = c("#6A040F","#9D0208","#E04A46","#DC2F02","#E85D04","#F48C06","#faa307","#f3e194")
```

```{r, include = F, message=F, warning=F}
df = read_csv("./data.csv")
df
```
```{r}
names(df)[2:dim(df)[2]]
df %>% group_by(`Purchase frequency`) %>% count()


highchart() %>%
    hc_add_series(plt1,
                  hcaes(x = Gender,
                        y = INVENTORY,
                        group = year,
                        colors = year
                        ), type = "column") %>% 
  hc_xAxis(categories = col_plt1$Gender %>% unique()) %>%
  hc_legend(verticalAlign = 'top', enabled = T) %>% 
  hc_title(text = "inventory by <b>Gender</b>", style = (list(fontSize = '14px')))  
    
```


Question 1 
=======================================================================

Row {data-heights=425 .colored }
-----------------------------------------------------------------------

### intro 1.1

this analysis including two parts. the first parts data is from the second sheet of the excel.it tells a story about how is the annually differences regarding to  `Gender` and `Division`. <br> 
and illustrates the overall sale performance regarding to stores and sku by using bubble charts, which could be related to future sales strategies. correlation plot is designed to tell the correlations between those key factors, it could tell more with more characteristics. t-test is developed to show if new stores have better performance in sales.

### inventory by gender
```{r, echo = F}
# col_plt2$variable = col_plt2$variable %>% as.character()
# col_plt2 
highchart() %>%
    hc_add_series(col_plt1,
                  hcaes(x = Gender,
                        y = INVENTORY,
                        group = year,
                        colors = year
                        ), type = "column") %>% 
  hc_xAxis(categories = col_plt1$Gender %>% unique()) %>%
  hc_legend(verticalAlign = 'top', enabled = T) %>% 
  hc_title(text = "inventory by <b>Gender</b>", style = (list(fontSize = '14px')))  
    

```

### sales by gender

```{r, echo = F}
# col_plt1
highchart() %>%
    hc_add_series(col_plt1,
                  hcaes(x = Gender,
                        y = SALES,
                        group = year,
                        colors = year
                        ), type = "column") %>% 
  hc_xAxis(categories = col_plt1$Gender %>% unique()) %>%
  hc_legend(verticalAlign = 'top', enabled = T) %>% 
  hc_title(text = "SALES by <b>Gender</b>", style = (list(fontSize = '14px')))  
    
 

```

Row {data-width=625 .colored }
-----------------------------------------------------------------------

### sales by division

```{r, echo = F}
# col_plt2
highchart() %>%
    hc_add_series(col_plt2,
                  hcaes(x = Division,
                        y = SALES,
                        group = year,
                        colors = year
                        ), type = "column") %>% 
  hc_xAxis(categories = col_plt2$Division %>% unique()) %>%
  hc_legend(verticalAlign = 'top', enabled = T) %>% 
  hc_title(text = "SALES by <b>Division</b>", style = (list(fontSize = '14px')))  


```

### inventory by division

```{r, echo = F}
# col_plt2
highchart() %>%
    hc_add_series(col_plt2,
                  hcaes(x = Division,
                        y = INVENTORY,
                        group = year,
                        colors = year
                        ), type = "column") %>% 
  hc_xAxis(categories = col_plt2$Division %>% unique()) %>%
  hc_legend(verticalAlign = 'top', enabled = T) %>% 
  hc_title(text = "INVENTORY by <b>Division</b>", style = (list(fontSize = '14px')))  


```


Row {.tabset-fade data-heights=325 .colored }
-----------------------------------------------------------------------

### top 10 sales&inventory on storeNo.(Old vs New)

```{r, echo = F}
plt1_bb = df_q12 %>% 
  group_by(StoreNo., year) %>% 
  summarise(sales = sum(SALES), inventory = sum(INVENTORY))
# plt1_bb = plt1_bb[plt1_bb$ProductNo.!= "OTHERS",]
plt1_bb = plt1_bb[plt1_bb$sales != 0,]
ty = plt1_bb[plt1_bb$year == 'this year', ]$StoreNo.
ly = plt1_bb[plt1_bb$year != 'this year', ]$StoreNo.
classic = ty[ty %in% ly]
new = ty[!ty %in% ly]

plt1_classic = plt1_bb[plt1_bb$StoreNo. %in% classic,]
plt1_classic$new = "classic"
plt1_cl_ttest = plt1_classic[plt1_classic$year == "this year", ]


plt1_classic= plt1_classic[plt1_classic$StoreNo. %in% 
               (plt1_classic %>% 
  arrange(desc(sales)) %>% head(10))$StoreNo., ]

plt1_new = plt1_bb[!plt1_bb$StoreNo. %in% classic,]
plt1_new$new = "new"
plt1_new_ttest = plt1_new
plt1_new = plt1_new %>% arrange(desc(sales)) %>% head(10)
# 



plot_ly(data = plt1_classic, x = ~StoreNo., y = ~inventory, z = ~sales,
        type = 'scatter3d', 
        color = ~year,
        # symbol = ~code,
        colors = viridis(45,alpha = .6),
        mode = 'markers',
        marker = list(size = ~ log(sales), opacity = .7)) %>%
  add_trace(data = plt1_new, x = ~StoreNo., y = ~inventory, z = ~sales,
            type = 'scatter3d', 
        color = ~new,
        # symbol = C,
        colors = viridis(45,alpha = .6),
        mode = 'markers',
        marker = list(size = ~ log(sales), opacity = .7, symbol = "diamond")
        # symbol = list("square")
        ) %>%
  layout(showlegend = FALSE, 
         title ="sales&inventory on storeNo.")
#  
```


### top 10 sales&inventory on SKU (Classic vs New)
```{r, echo = F}
# df_q12
plt1_bb = df_q12 %>% 
  group_by(ProductNo., year) %>% 
  summarise(sales = sum(SALES), inventory = sum(INVENTORY))
plt1_bb = plt1_bb[plt1_bb$ProductNo.!= "OTHERS",]
plt1_bb = plt1_bb[plt1_bb$sales != 0,]
ty = plt1_bb[plt1_bb$year == 'this year', ]$ProductNo.
ly = plt1_bb[plt1_bb$year != 'this year', ]$ProductNo.
# plt1_bb[plt1_bb$ProductNo. == "SKU1887",]
classic = ty[ty %in% ly]
new = ty[!ty %in% ly]

plt1_classic = plt1_bb[plt1_bb$ProductNo. %in% classic,]
plt1_classic$new = "classic"
ttst2 = plt1_classic[plt1_classic$year == 'this year', ]

plt1_classic= plt1_classic[plt1_classic$ProductNo. %in% 
               (plt1_classic %>% 
  arrange(desc(sales)) %>% head(10))$ProductNo., ]

plt1_new = plt1_bb[!plt1_bb$ProductNo. %in% classic,]
plt1_new$new = "new"
ttst22 = plt1_new
plt1_new = plt1_new %>% arrange(desc(sales)) %>% head(10)

# 
# plt1_bb = rbind(plt1_classic, plt1_new)
 
plot_ly(data = plt1_classic, x = ~ProductNo., y = ~inventory, z = ~sales,
        type = 'scatter3d', 
        color = ~year,
        # symbol = "diamond",
        colors = viridis(45,alpha = .6),
        mode = 'markers',
        marker = list(size = ~ log(sales), opacity = .7)) %>%
  add_trace(data = plt1_new, x = ~ProductNo., y = ~inventory, z = ~sales,
            type = 'scatter3d', 
        color = ~new,
        # symbol = C,
        colors = viridis(45,alpha = .6),
        mode = 'markers',
        marker = list(size = ~ log(sales), opacity = .7, symbol = "diamond")
        # symbol = list("square")
        ) %>% 
  layout(showlegend = FALSE, 
         title ="sales&inventory on SKU")
 
```

Row {.tabset-fade data-heights=325 .colored }
-----------------------------------------------------------------------

### cor

```{r, echo = F}
# df_q12
cor = df_q12[6:dim(df_q12)[2]] %>%cor()%>% data.frame()
m = cor %>% as.matrix()
x = cor %>% names() 
# matrix(rnorm(9), nrow = 3, ncol = 3)
fig <- plot_ly(x = x, y = x, 
    z = m, type = "heatmap", colors= viridis::plasma(16,.1,.3)
) %>% layout(title = "correlations")

fig
```

### test

```{r, echo = F}
# library(car)
# ?linearHypothesis()
ttst = rbind(plt1_cl_ttest, plt1_new_ttest)
t.test(sales ~ new, data = ttst )
print("the new stores showed insignificant difference in sales compare to old stores")
# 
# ttest2 = rbind(ttst2, ttst22)
# t.test(sales ~ new, data = ttest2 )
# print("the new stores showed insignificant difference in sales compare to old stores")

```

---

Column {data-heights=10 data-width=10}
-----------------------------------------------------------------------

### intro 1.2

below used data from first sheet in Q1, look detailly on specific time span comparison
17 appears to have better sales / transaction / traffic data than 16, the overall performance in year 17 is not explainable from the dataset, we can on jump into a conclusion that NIKE's business is earning more from year to year. the following detailed data would show us the evidence from every aspect in this dataset

Column {.tabset .tabset-fade data-heights=625 data-width=625 .colored }
-----------------------------------------------------------------------

### traffic comparison 16~17

```{r, echo = F}

highchart() %>% 
    hc_add_series(plt2, 
                  hcaes(x = as.character(date), 
                        y = traffic,
                        group = year, 
                        color = year), type = "line") %>%  # # series.name and series.color 
  hc_tooltip(crosshairs = TRUE, borderWidth = 1.5,pointFormat = 
                paste(
                  "storetype: <b>{series.name}<b> <br> traffic: <b>{point.y:.2f}<b>" 
                 )) %>%  hc_title(text = "traffic comparison 16~17") 


# df11 %>% head()
# paste0((plt1 %>% names())[4:7][1])
```

### transaction comparison 16~17

```{r,echo = F}
# transaction), sales_amt = sum(sales_amt), sold_unit = sum(sold_unit))
highchart() %>% 
    hc_add_series(plt2, 
                  hcaes(x = as.character(date), 
                        y = transaction,
                        group = year, 
                        color = year), type = "line") %>%  # # series.name and series.color 
  hc_tooltip(crosshairs = TRUE, borderWidth = 1.5,pointFormat = 
                paste(
                  "storetype: <b>{series.name}<b> <br> transaction: <b>{point.y:.2f}<b>" 
                 ))   %>%  hc_title(text = "transaction comparison 16~17") 

```

### sales_amt comparison 16~17

```{r,echo = F}
# transaction), sales_amt = sum(sales_amt), sold_unit = sum(sold_unit))
highchart() %>% 
    hc_add_series(plt2, 
                  hcaes(x = as.character(date), 
                        y = sales_amt,
                        group = year, 
                        color = year), type = "line") %>%  # # series.name and series.color 
  hc_tooltip(crosshairs = TRUE, borderWidth = 1.5,pointFormat = 
                paste(
                  "storetype: <b>{series.name}<b> <br> sales_amt: <b>{point.y:.2f}<b>" 
                 ))  %>%  hc_title(text = "sales_amt comparison 16~17") 

```


### sold_unit comparison 16~17

```{r,echo = F}
# transaction), sales_amt = sum(sales_amt), sold_unit = sum(sold_unit))
highchart() %>% 
    hc_add_series(plt2, 
                  hcaes(x = as.character(date), 
                        y = sold_unit,
                        group = year, 
                        color = year), type = "line") %>%  # # series.name and series.color 
  hc_tooltip(crosshairs = TRUE, borderWidth = 1.5,pointFormat = 
                paste(
                  "storetype: <b>{series.name}<b> <br> sold_unit: <b>{point.y:.2f}<b>" 
                 ))  %>%  hc_title(text = "sold_unit comparison 16~17") 

```

Row {data-heights=700 data-width=625 .no-padding .colored}
-------------------------------------

```{r, echo = F}
 
fig <- plot_ly()
 

for (i in 1:4){
 
    pp = plt1[plt1$year == '2016',] %>% select((plt1 %>% names())[4:7][i])
    names(pp) = c("store_type", 'date', 'value')
    fig = fig %>% 
          add_pie(data =  pp, 
              labels = ~store_type, 
              values = ~value,
              hole = .4,
              textinfo = 'label+percent',
              textposition = 'inside',
              # hoverinfo = 'text',
              # text = ~paste0(bms_industry, sum_bill_amount),
              name = paste0("2016",(plt1 %>% names())[4:7][i]) ,
              domain = list(row = 0, column = i-1),
              marker = list(colors = 
                              inferno(8, begin  = .2, end = .8,
                                      direction = -1),
                          line = list(color = '#FFFFFF', width = 1)),
            showlegend = T) %>% layout(title= paste0((plt1 %>% names())[4:7][i]))
    i = i+1
   
}

for (i in 1:4){

   
    pp = plt1[plt1$year == '2017',] %>% select((plt1 %>% names())[4:7][i])
    names(pp) = c("store_type", 'date', 'value')
    fig = fig %>% 
          add_pie(data =  pp, 
              labels = ~store_type, 
              values = ~value,
              hole = .4,
              textinfo = 'label+percent',
              textposition = 'inside',
              # hoverinfo = 'text',
              # text = ~paste0(bms_industry, sum_bill_amount),
              name =  paste0("2017",(plt1 %>% names())[4:7][i]) ,
              domain = list(row = 1, column = i-1),
              marker = list(colors = 
                              inferno(8, begin  = .2, end = .8,
                                      direction = -1),
                          line = list(color = '#FFFFFF', width = 1)),
            showlegend = T) %>% layout(title= paste0((plt1 %>% names())[4:7][i]))
    i = i+1

}
 
fig <- fig %>% layout(title = "16&17 key value comparison",
                      showlegend = F,
                      grid=list(rows=2, columns=4),
                      xaxis = list(
                        showgrid = FALSE, 
                        zeroline = FALSE, 
                        showticklabels = FALSE),
                      yaxis = list(
                        showgrid = FALSE, 
                        zeroline = FALSE, 
                        showticklabels = FALSE))

fig
```


### insight
 
comparing to 2016 (4 pie charts on the upper part), roughly speaking that `sport_performance` business has been replaced by `flagship` as largest business in 2017 (4 pie charts on the lower part) , in this dataset.




Question 2 predictions (in another doc: nikeq2.html)
=======================================================================

<br>
(in another doc: nikeq2.html)

Question 3 causal inferences 
=======================================================================


Row {data-heights=700 data-width=125 .no-padding .colored}
-------------------------------------
 
### data walkthrough

```{r, include = F}

df31 = readxl::read_excel("Question3.xlsx", sheet = 1) 
# df32 = readxl::read_excel("Question3.xlsx", sheet = 2, skip = 3, col_names = F)
```

```{r, echo=F}
cnt31 = apply(df31, 2, function(x) length(unique(x))) %>% data.frame()
names(cnt31) = 'count_distinct'
dropcol = rownames(cnt31)[which(cnt31$count_distinct == 1)]
df31 = df31 %>% select(-dropcol)
datatable(cnt31)
```


Row {data-heights=1000 data-width=1000 .no-padding .colored}
-------------------------------------

### correlation plot
```{r, echo = F, warning=F, message=F, echo = F}
# df31
library(data.table)
cor = df31[!df31 %>% names() %like% "COLOR"]
cor = cor[,2:dim(cor)[2]] %>%cor()%>% data.frame()
m = cor %>% as.matrix()
x = cor %>% names() 
# matrix(rnorm(9), nrow = 3, ncol = 3)
fig <- plot_ly(x = x, y = x, 
    z = m, type = "heatmap", colors= viridis::plasma(16,.1,.3)
) %>% layout(title = "correlations")
fig
```


Row {data-heights=700 data-width=625 .no-padding .colored}
-------------------------------------

### regressions

```{r, warning = F, message = F, results='asis', echo=F}
# df31 %>% group_by()
# df31
fixed_eff = df31[df31 %>% names() %like% "IF"] %>% names()
fixed_eff = fixed_eff %>% append(c("COLOR_CD_1", "COLOR_CD_2", "COLOR_CD_3"))
paras = df31[!df31 %>% names() %in% fixed_eff] %>% names()
paras = paras[3:length(paras)]

para_str = paste(paras, collapse="+")
fe_str =  paste(fixed_eff, collapse="+") 
fml1 = as.formula(paste("SALES_QTY~", para_str,
                        "-1-SSNRK_1ST_SKU_LAUNCH-NUM_COLOR_DESC -LAST_SEASON_INDICATOR",
                        "|", fe_str
                        ))
reg1 = felm(fml1, data = df31) 
print(fml1)
print(
  "
  "
)
stargazer(reg1, type = "html")
```

### memos

this is a fixed effect model by using felm function from car package, the categorical variables are suppressed in fixed-effects, they are considered but not included in the output report, the formula has shown above, three parameters are eliminated due to vacancy in value caused by `Multicollinearity`.

the significant variables including:

`SEASON_SINCE_1ST_SKU_LAUNCH` which means Number of seasons since the SKU was launched, 10 more sales for an extra season. 


`NUMSKU_SAME_STYLE_IN1SSN` Number of products with the same style, popular styles can be more welcomed in our market. `NUMSKU_SAME_PF_IN1SSN` (Number of products with the same power franchise) also statistically significant. however `NUMSKU_SAME_MODEL_IN1SSN` not significant, which implys model is not a key role in this dataset.


`OMD_DAYS_SINCE_SEASON_BEGIN` Number of days since SKU launch in the season, has a negative value and statistically significant. which means in a season, the SKU can become more unpopular from day to day.



Row {data-heights=500 data-width=505 .no-padding .colored}
-------------------------------------

### rough regression on categorical variables

```{r, echo = F, warning = F, results='asis'}
# para_str
# df31[paras]
library(lme4)
# fe_str
fm2 = as.formula(paste("SALES_QTY~0+",fe_str))
reg2 = felm(fm2, data = df31) 
print(fm2)
print(
  "
  "
)
stargazer(reg2, type = "html")
```



### memos

categorical variables only regression, the formula has shown above, parameters are eliminated due to vacancy in value caused by `Multicollinearity`.

significant variables are:

`IF_GENERAL_PRICE`
`IF_TRIPLEWHITE`
`IF_SEASONAL_SILO_SU`                                             
`IF_NEW_SEASONAL`

which indicates that: 
basically customers are focusing on two things: the price and if the sku is new. there are two more colors go significant, but the potential color ~ price relation is not clear.


info
==========================================================

###

Credit to Siming Yan. Data credit to Nike china. Developed by R language and plotly, highcharter, flexdashboard. Second study developed by python, with facebook Prophet and Sklearn. 

This Notebook is not released to any platform but under the Apache 2.0 open source license.