---
title: "Siemens_report"
author: "Siming Yan"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    highlight: tango
    theme: cerulean
    toc: yes
    toc_float: yes
---

<style>
.colored {
  background-color: #FAFAFA;
}
</style>



``` {js, include = F}
// Inverse color of navigation bar.
$('.navbar-inverse').removeClass('navbar-inverse').addClass('navbar-default');
```

```{r setup, include = FALSE}
 
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)

```

```{r setup2, include=FALSE}
# library(flexdashboard)
library(tidyverse)
library(reshape2)
library(lubridate)
library(highcharter) # Interactive data visualizations
library(viridis)
library(DT)
library(lfe)
library(stargazer)
library(tidyverse)
library(stringr)
library(lubridate)
library(zoo)
library(forecast)
library(Hmisc) 
library(xts)
library(reticulate)
library(plotly)
library(lme4)
library(aod)
# reticulate::use_condaenv("siming")
# vignette("highcharter")
# vignette("highcharts-api")
```


```{r, include=FALSE}
# Create a custom theme for the plots. 
custom_theme <- hc_theme(
  colors = c('#5CACEE', '#ee9e5c','#eee75c', '#5ceee7'),
  chart = list(
         backgroundColor = '#FAFAFA', 
         plotBorderColor = "black"),
  xAxis = list(
         gridLineColor = "E5E5E5", 
         labels = list(style = list(color = "#333333")), 
         lineColor = "#E5E5E5", 
         minorGridLineColor = "#E5E5E5", 
         tickColor = "#E5E5E5", 
         title = list(style = list(color = "#333333"))), 
  yAxis = list(
         gridLineColor = "#E5E5E5", 
         labels = list(style = list(color = "#333333")), 
         lineColor = "#E5E5E5", 
         minorGridLineColor = "#E5E5E5", 
         tickColor = "#E5E5E5", 
         tickWidth = 1, 
         title = list(style = list(color = "#333333"))),   
  title = list(style = list(color = '#333333', fontFamily = "Lato")),
  subtitle = list(style = list(color = '#666666', fontFamily = "Lato")),
  legend = list(
         itemStyle = list(color = "#333333"), 
         itemHoverStyle = list(color = "#FFF"), 
         itemHiddenStyle = list(color = "#606063")), 
  credits = list(style = list(color = "#666")),
  itemHoverStyle = list(color = 'gray'))
kbt <- function(...){
  knitr::kable(..., format.args = list(big.mark = ',', scientific = F)) %>%
    kableExtra::kable_styling(c("striped", "condensed"),
                               full_width = F,
                               position = "center",
                               row_label_position = "c") %>%
   row_spec(0, bold = T)
}

stg <- function(...){
  stargazer::stargazer(..., 
          type = "text",
          # style = "qje",
          # title = "daily_kwh ~ post:encouraged|customer_id + no.bill|0|customer_id",
          keep.stat = c("n", "ser"),
          digits = 5)
}

parent_cat1 = c("#6A040F","#9D0208","#E04A46","#DC2F02","#E85D04","#F48C06","#faa307","#f3e194")
#
```

```{r, include = F, message=F, warning=F}
ld = function(){
    
  df = read_csv("./data.csv")
  names(df) = gsub(" ", '_',names(df) )
  
  df$Distributor_customer = df$Distributor_customer %>% as.factor()
  levels(df$Distributor_customer) = c(0,1)
  df$Other_products = df$Other_products %>% as.factor()
  levels(df$Other_products) = c(0,1)
  df$Industry = df$Industry %>% as.factor()
  return(df)
}

df = ld()
df %>% dim()
```

# What kinds of customer Siemens should target for product Y.


## check out the distribution of the given dataset.

```{r, echo = F} 

nmlist = names(df)[2:dim(df)[2]]
fig <- plot_ly()
for (i in 1:4){
    # name = nmlist[i]
    pp = df %>% group_by(df[nmlist[i]]) %>% count()
    fig = fig %>% 
          add_pie(data =  pp, 
              labels = pp[nmlist[i]], 
              values = ~n,
              hole = .4,
              textinfo = 'label+percent',
              textposition = 'inside',
              # hoverinfo = 'text',
              name = paste0((pp %>% names())[1]) ,
              domain = list(row = 0, column = i-1),
              marker = list(colors = 
                              inferno(8, begin  = .2, end = .8,
                                      direction = -1),
                          line = list(color = '#FFFFFF', width = 1)),
            showlegend = T) 
      # add_annotations(text= paste0((pp %>% names())[1]))
    i=1+i
   
}

for (i in 5:8){
    # name = nmlist[i]
    pp = df %>% group_by(df[nmlist[i]]) %>% count()
    fig = fig %>% 
          add_pie(data =  pp, 
              labels = pp[nmlist[i]], 
              values = ~n,
              hole = .4,
              textinfo = 'label+percent',
              textposition = 'inside',
              # hoverinfo = 'text',
              name = paste0((pp %>% names())[1]) ,
              domain = list(row = 1, column = i-5),
              marker = list(colors = 
                              inferno(8, begin  = .2, end = .8,
                                      direction = -1),
                          line = list(color = '#FFFFFF', width = 1)),
            showlegend = T) 
      # add_annotations(text = paste0((pp %>% names())[1]))
    i=1+i
   
}
#  
fig <- fig %>% layout(title = "features distribution",
                      showlegend = F,
                      grid=list(rows=2, columns=4),
                      xaxis = list(
                        showgrid = FALSE, 
                        zeroline = FALSE, 
                        showticklabels = FALSE),
                      yaxis = list(
                        showgrid = FALSE, 
                        zeroline = FALSE, 
                        showticklabels = FALSE))

fig
```



## corr

```{r, echo = F}

cor_plt = function(df){
  
  df$Distributor_customer = df$Distributor_customer %>% as.numeric()
  df$Other_products = df$Other_products %>% as.numeric()
  df$Industry = df$Industry %>% as.numeric()
  cor = df[2:dim(df)[2]] %>% cor() %>% data.frame()
  m = cor %>% as.matrix()
  x = cor %>% names() 
  # matrix(rnorm(9), nrow = 3, ncol = 3)
  fig <- plot_ly(x = x, y = x, 
      z = m, type = "heatmap", colors= viridis::plasma(16,.1,.3)
  ) %>% layout(title = "correlations")
  
  fig
}

# 

cor_plt(df)
```

## model selection

#### base line and ramsey reset test 

```{r}
# naive model
m1 = lm( Purchase_frequency~
         Distributor_customer+
         Year_being_customer+
         Other_products+
         Satisfaction+
         Awareness_of_competitor +
         Competitor_shares + Industry, data = df)



library(lmtest)
resettest(m1, power=2:4, type="regressor")
resettest(m1, power=2:4, type="fitted")
```

fail to reject the null hypothesis of None omitted variable error. hence need to power up parameters.

```{r}
# interactive model
m2 = lm( Purchase_frequency~
         Distributor_customer+
         Other_products+
         Year_being_customer*
         Satisfaction+
         Awareness_of_competitor*
         Competitor_shares + Industry, data = df)
# rank 1 best model.
m3 = lm( Purchase_frequency~ 
         Year_being_customer+ 
         Satisfaction+
         Awareness_of_competitor +
         Competitor_shares , data = df)

resettest(m3, power=2, type="fitted")
# rank 2
m4 = lm( Purchase_frequency~ 
         Year_being_customer+
         # I(Year_being_customer^2) +
         # Satisfaction+
         I(Satisfaction^2)+
         Awareness_of_competitor +
         # I(Awareness_of_competitor^2)+
         # Competitor_shares
         I(Competitor_shares^2)
         , data = df)
# BIC(m4)

m5 = lmer(Purchase_frequency ~ 
                    1 +
                    (Year_being_customer+
                       I(Satisfaction^2)+
                       Awareness_of_competitor + 
                       I(Competitor_shares^2)||
                       Industry),
                  data=df) 
m6 = lmer(Purchase_frequency ~ 
                    (Year_being_customer+
                       I(Satisfaction^2)+
                       Awareness_of_competitor +
                       I(Competitor_shares^2) +
                       Other_products:I(Satisfaction^2)||
                       Industry),
                  data=df)
 
# 1 + age:Sex + (1|Subject)/
AIC(m1,m2,m3,m4,m5,m6) %>% cbind(BIC(m1,m2,m3,m4,m5,m6) ) %>%
  datatable()

```

## linear model with fixed effect and clustered error 

```{r}
df$Industry = factor(df$Industry) 
reg1 = felm(
  Purchase_frequency~
         Distributor_customer+
         Year_being_customer+
         Other_products+
         I(Satisfaction^2)+
         Awareness_of_competitor +
         I(Competitor_shares^2) 
         # Other_products:Satisfaction + 
         # Other_products:Satisfaction
  |Industry|0|Industry, data = df)
reg1 %>% stg()

# stargazer(reg1, type = "html")
```


```{r, echo = F}
#  
# reg_plt = function(df_reg){
#   df_reg$Satisfaction2 = df_reg$Satisfaction^2
#   
#   reg12 = lm(Purchase_frequency~
#            # Distributor_customer+
#            Year_being_customer+
#            # Other_products+
#              Satisfaction+
#            I(Satisfaction)^2, df_reg)
# 
#   axis_x <- seq(min(df_reg$Year_being_customer), 
#                 max(df_reg$Year_being_customer), by = 2)
#   axis_y <- seq(min(df_reg$Satisfaction), 
#                 max(df_reg$Satisfaction), by = 2)
#   
#   
#   # axis_x
#   petal_lm_surface <- expand.grid(
#     Year_being_customer = axis_x, 
#     Satisfaction = axis_y, 
#     KEEP.OUT.ATTRS = F)
#   
#   petal_lm_surface$Petal.Length <- predict.lm(
#     reg12, newdata = petal_lm_surface)
#   
#   petal_lm_surface <- acast(
#     petal_lm_surface, 
#     Satisfaction~Year_being_customer, value.var = "Petal.Length") 
#   # y ~ x
#   
#    
#   iris_plot <- plot_ly(df_reg, 
#                        x = ~Year_being_customer, 
#                        y = ~Satisfaction, 
#                        z = ~Purchase_frequency,
#                        # text = ~Species, # EDIT: ~ added
#                        type = "scatter3d", 
#                        mode = "markers",
#                        color = 'Satisfaction2',
#                        colors = cividis(1055, begin = .3, end = .9)
#                        # marker = list(color = hcolors)
#                        ) %>% 
#     layout(showlegend = F) 
#   
#   iris_plot <- add_trace(p = iris_plot,
#                          z = petal_lm_surface,
#                          x = axis_x,
#                          y = axis_y,
#                          type = "surface")  %>% 
#     layout(showlegend = F)
#   return(iris_plot)
# }
# df

plot_ly(data = df, 
        x = ~Year_being_customer, 
        y = ~Satisfaction, z = ~Purchase_frequency,
        type = 'scatter3d', 
        color = ~Satisfaction,
        symbol = ~Distributor_customer,
        colors = viridis(45,alpha = .6),
        mode = 'markers',
        marker = list(
          size = ~Satisfaction^2, opacity = .7)) %>%
  layout(showlegend = FALSE, 
         title ="single bms_amount by fee type and customer code")

# reg_plt(df)

```


## linear mixed effect model

```{r, warning = F, message=F}

mod <- lme4::lmer(Purchase_frequency ~ 1 + 
                    (Year_being_customer+
                       I(Satisfaction^2)+
                       Awareness_of_competitor + 
                       I(Competitor_shares^2)||Industry),
                  data=df)
# summary(mod) 
# confint(mod)
```


```{r, warning = F, message=F, echo = F}
# styleColorBar2 <- function (data, color1, color2) 
#   {
#     M <- max(abs(data), na.rm = TRUE)
#     js <- c(
#       "value <= 0 ? ",  
#       sprintf("'linear-gradient(90deg, transparent ' + (1+value/%f) * 100 + '%%, %s ' + (1+value/%f) * 100 + '%%)'", 
#               M, color1, M),
#       " : ",
#       sprintf("'linear-gradient(90deg, transparent ' + (1-value/%f) * 100 + '%%, %s ' + (1-value/%f) * 100 + '%%)'", 
#               M, color2, M) 
#     )
#     JS(js)
# }

table_out1 = coef(mod)$Industry
brks <- quantile(table_out1, 
                 probs = seq(.05, .95, .05), na.rm = TRUE)
clrs <- round(seq(255, 40, length.out = length(brks) + 1), 0) %>%
  {paste0("rgb(255,", ., ",", ., ")")}


table_out1 %>% round(3) %>%  datatable(
  options = list(
  autoWidth = F,
  columnDefs = list(list(width = '20px', targets = c(1, 3)))
  )) %>% 
  formatStyle(names(table_out1), 
              backgroundColor = styleInterval(brks, clrs)) 
```
 
 
 
## auto ml


```{r, include = F}
library(h2o)
df = ld()
h2o.init()
df = df %>% select(-Index)
df = mutate(df, Purchase_frequency = ifelse(Purchase_frequency>0, 1, 0)) 
df$Purchase_frequency = df$Purchase_frequency %>% as.factor()
# set the predictor and response columns
predictors <- names(df)[!names(df) %in% "Purchase_frequency"]
response <- "Purchase_frequency" 
df_splits <- h2o.splitFrame(data =  as.h2o(df), ratios = 0.8, seed = 1234)
train <- df_splits[[1]]
test <- df_splits[[2]]
```


```{r, include=F}
# build a GLM model
# prostate_glm <- h2o.glm(family = "binomial",
#                         x = predictors,
#                         y = response,
#                         training_frame = train,
#                         lambda = 0,
#                         compute_p_values = TRUE)
# 
# # predict using the GLM model and the testing dataset
# predict <- h2o.predict(object = prostate_glm, newdata = test)
# perf = h2o.performance((prostate_glm))
# test_df = test %>% as.data.frame()
# h2o.varimp(prostate_glm)
# 
# h2o.precision(perf)
# perf
#  
# cbind(test_df$Purchase_frequency, 
#       (predict %>% as.data.frame())) 
#  

```

```{r, echo=F, message = F, include=F}
aml <- h2o.automl(x = predictors,
                  y = response,
                  training_frame = train,
                  max_models = 5,
                  seed = 529,
                  verbosity = "warn")

# View the AutoML Leaderboard
lb <- aml@leaderboard
# print(lb, n = nrow(lb))
# lb

```

```{r, echo = F}

h2o.explain(aml@leader, test)
perf  = h2o.performance(aml@leader, test)
perf

```

