---
title: "nike_report"
author: "Siming Yan"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    # css: bootstrap.min.css
    theme: yeti
---

<style>
.colored {
  background-color: #FAFAFA;
}
</style>



``` {js}
// Inverse color of navigation bar.
$('.navbar-inverse').removeClass('navbar-inverse').addClass('navbar-default');
```

```{r setup, include = FALSE}
 
knitr::opts_chunk$set(echo = TRUE)

```

```{r setup2, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(reshape2)
library(lubridate)
library(highcharter) # Interactive data visualizations
library(viridis)
library(DT)
library(lfe)
library(stargazer)
library(tidyverse)
library(stringr)
library(lubridate)
library(zoo)
library(forecast)
library(Hmisc) 
library(xts)
library(reticulate)
library(plotly)
# reticulate::use_condaenv("siming")
# vignette("highcharter")
# vignette("highcharts-api")
```


```{r, include=FALSE}
# Create a custom theme for the plots. 
custom_theme <- hc_theme(
  colors = c('#5CACEE', '#ee9e5c','#eee75c', '#5ceee7'),
  chart = list(
         backgroundColor = '#FAFAFA', 
         plotBorderColor = "black"),
  xAxis = list(
         gridLineColor = "E5E5E5", 
         labels = list(style = list(color = "#333333")), 
         lineColor = "#E5E5E5", 
         minorGridLineColor = "#E5E5E5", 
         tickColor = "#E5E5E5", 
         title = list(style = list(color = "#333333"))), 
  yAxis = list(
         gridLineColor = "#E5E5E5", 
         labels = list(style = list(color = "#333333")), 
         lineColor = "#E5E5E5", 
         minorGridLineColor = "#E5E5E5", 
         tickColor = "#E5E5E5", 
         tickWidth = 1, 
         title = list(style = list(color = "#333333"))),   
  title = list(style = list(color = '#333333', fontFamily = "Lato")),
  subtitle = list(style = list(color = '#666666', fontFamily = "Lato")),
  legend = list(
         itemStyle = list(color = "#333333"), 
         itemHoverStyle = list(color = "#FFF"), 
         itemHiddenStyle = list(color = "#606063")), 
  credits = list(style = list(color = "#666")),
  itemHoverStyle = list(color = 'gray'))


parent_cat1 = c("#6A040F","#9D0208","#E04A46","#DC2F02","#E85D04","#F48C06","#faa307","#f3e194")
```

```{r, include = F, message=F, warning=F}
q11 = readxl::read_excel("Question 1.xlsx", sheet = 1 , skip = 1)
q11_fixed_col = q11[,1:3]
q11_fixed_col['Date'] = q11_fixed_col['Date'] %>% lapply(FUN = 'as.Date')
q11_fixed_col2 = q11_fixed_col
q11_fixed_col2['minus1'] = years(1)
q11_fixed_col2['Date'] = q11_fixed_col2['Date'] - q11_fixed_col2['minus1'] 
q11_fixed_col2 = q11_fixed_col2 %>% subset(select  = -c(minus1))
names(q11_fixed_col) = c('store_no','store_type','date')
names(q11_fixed_col2)= c('store_no','store_type','date')
df_q11 = rbind(q11_fixed_col, q11_fixed_col2) 
q11_fixed_col = q11[, 4:7]
q11_fixed_col2 = q11[, 8:11]
names(q11_fixed_col) = c("traffic", "transaction", "sales_amt", "sold_unit") 
names(q11_fixed_col2) = c("traffic", "transaction", "sales_amt", "sold_unit") 
df_q112 = rbind(q11_fixed_col, q11_fixed_col2) 
df11 =  cbind(df_q11 , df_q112)
df11['sales_amt']
df11['sales_amt'] = df11['sales_amt'] %>% sapply(as.numeric)
df11 = df11 %>% drop_na()  
df11['year'] = df11['date'] %>% sapply(str_sub,1,4)
```


```{r, include=F}
q12 = readxl::read_excel("Question 1.xlsx", sheet = 2)
# q12 = q12 %>% select(-`Product No.`)
q12['year'] = 'this year'
q12_fixed_col = q12[,c(1:4, dim(q12)[2])] 
q12_fixed_col2 = q12_fixed_col
q12_fixed_col2['year'] = 'last year' 
df_q12 = rbind(q12_fixed_col, q12_fixed_col2) 
q121 = q12[, 5:8]
q122 = q12[,9:12]
names(q122) = names(q121) 
df_q12 = cbind(df_q12,rbind(q121,q122))
names(df_q12) =gsub('TY | ','', names(df_q12))
 #
```



Question 1 
=======================================================================

```{r, echo = F, message=F,warning=F}
plt1 = df11 %>% 
  group_by(store_type,date,year) %>% 
  summarise(traffic = sum(traffic), transaction= sum(transaction), sales_amt = sum(sales_amt), sold_unit = sum(sold_unit))
plt2 = df11 %>% group_by(date,year) %>% summarise(traffic = sum(traffic), transaction= sum(transaction), sales_amt = sum(sales_amt), sold_unit = sum(sold_unit))

col_plt1 = df_q12 %>% group_by(Gender,year) %>% 
  summarise(INVENTUNIT = sum(INVENTUNIT), 
            INVENTORY= sum(INVENTORY), 
            SALES = sum(SALES), 
            UNITS = sum(UNITS))

col_plt2 = df_q12 %>% group_by(Division,year) %>% 
  summarise(INVENTUNIT = sum(INVENTUNIT), 
            INVENTORY= sum(INVENTORY), 
            SALES = sum(SALES), 
            UNITS = sum(UNITS))
# df_q12
# col_plt1
# col_plt1 = col_plt1 %>% melt()
# col_plt2= col_plt2 %>% melt()
# col_plt2
```



Row {data-heights=375 .colored }
-----------------------------------------------------------------------

### start

this analysis including two parts. the first parts data is from the second sheet of the excel.it tells a story about how is the annually differences regarding to  `Gender` and `Division`. <br> 
and illustrates the overall sale performance regarding to stores and sku by using bubble charts, which could be related to future sales strategies. correlation plot is designed to tell the correlations between those key factors, it could tell more with more characteristics. t-test is developed to show if new stores have better performance in sales.

### inventory by gender
```{r, echo = F}
# col_plt2$variable = col_plt2$variable %>% as.character()
# col_plt2 
highchart() %>%
    hc_add_series(col_plt1,
                  hcaes(x = Gender,
                        y = INVENTORY,
                        group = year,
                        colors = year
                        ), type = "column") %>% 
  hc_xAxis(categories = col_plt1$Gender %>% unique()) %>%
  hc_legend(verticalAlign = 'top', enabled = T) %>% 
  hc_title(text = "inventory by <b>Gender</b>", style = (list(fontSize = '14px')))  
    

```

### sales by gender

```{r, echo = F}
# col_plt1
highchart() %>%
    hc_add_series(col_plt1,
                  hcaes(x = Gender,
                        y = SALES,
                        group = year,
                        colors = year
                        ), type = "column") %>% 
  hc_xAxis(categories = col_plt1$Gender %>% unique()) %>%
  hc_legend(verticalAlign = 'top', enabled = T) %>% 
  hc_title(text = "SALES by <b>Gender</b>", style = (list(fontSize = '14px')))  
    
 

```

Row {data-width=625 .colored }
-----------------------------------------------------------------------

### sales by division

```{r, echo = F}
# col_plt2
highchart() %>%
    hc_add_series(col_plt2,
                  hcaes(x = Division,
                        y = SALES,
                        group = year,
                        colors = year
                        ), type = "column") %>% 
  hc_xAxis(categories = col_plt2$Division %>% unique()) %>%
  hc_legend(verticalAlign = 'top', enabled = T) %>% 
  hc_title(text = "SALES by <b>Division</b>", style = (list(fontSize = '14px')))  


```

### inventory by division

```{r, echo = F}
# col_plt2
highchart() %>%
    hc_add_series(col_plt2,
                  hcaes(x = Division,
                        y = INVENTORY,
                        group = year,
                        colors = year
                        ), type = "column") %>% 
  hc_xAxis(categories = col_plt2$Division %>% unique()) %>%
  hc_legend(verticalAlign = 'top', enabled = T) %>% 
  hc_title(text = "INVENTORY by <b>Division</b>", style = (list(fontSize = '14px')))  


```


Row {.tabset-fade data-heights=325 .colored }
-----------------------------------------------------------------------

### top 10 sales&inventory on storeNo.(Old vs New)

```{r, echo = F}
plt1_bb = df_q12 %>% 
  group_by(StoreNo., year) %>% 
  summarise(sales = sum(SALES), inventory = sum(INVENTORY))
# plt1_bb = plt1_bb[plt1_bb$ProductNo.!= "OTHERS",]
plt1_bb = plt1_bb[plt1_bb$sales != 0,]
ty = plt1_bb[plt1_bb$year == 'this year', ]$StoreNo.
ly = plt1_bb[plt1_bb$year != 'this year', ]$StoreNo.
classic = ty[ty %in% ly]
new = ty[!ty %in% ly]

plt1_classic = plt1_bb[plt1_bb$StoreNo. %in% classic,]
plt1_classic$new = "classic"
plt1_cl_ttest = plt1_classic[plt1_classic$year == "this year", ]


plt1_classic= plt1_classic[plt1_classic$StoreNo. %in% 
               (plt1_classic %>% 
  arrange(desc(sales)) %>% head(10))$StoreNo., ]

plt1_new = plt1_bb[!plt1_bb$StoreNo. %in% classic,]
plt1_new$new = "new"
plt1_new_ttest = plt1_new
plt1_new = plt1_new %>% arrange(desc(sales)) %>% head(10)
# 



plot_ly(data = plt1_classic, x = ~StoreNo., y = ~inventory, z = ~sales,
        type = 'scatter3d', 
        color = ~year,
        # symbol = ~code,
        colors = viridis(45,alpha = .6),
        mode = 'markers',
        marker = list(size = ~ log(sales), opacity = .7)) %>%
  add_trace(data = plt1_new, x = ~StoreNo., y = ~inventory, z = ~sales,
            type = 'scatter3d', 
        color = ~new,
        # symbol = C,
        colors = viridis(45,alpha = .6),
        mode = 'markers',
        marker = list(size = ~ log(sales), opacity = .7, symbol = "diamond")
        # symbol = list("square")
        ) %>%
  layout(showlegend = FALSE, 
         title ="sales&inventory on storeNo.")
#  
```


### top 10 sales&inventory on SKU (Classic vs New)
```{r, echo = F}
# df_q12
plt1_bb = df_q12 %>% 
  group_by(ProductNo., year) %>% 
  summarise(sales = sum(SALES), inventory = sum(INVENTORY))
plt1_bb = plt1_bb[plt1_bb$ProductNo.!= "OTHERS",]
plt1_bb = plt1_bb[plt1_bb$sales != 0,]
ty = plt1_bb[plt1_bb$year == 'this year', ]$ProductNo.
ly = plt1_bb[plt1_bb$year != 'this year', ]$ProductNo.
# plt1_bb[plt1_bb$ProductNo. == "SKU1887",]
classic = ty[ty %in% ly]
new = ty[!ty %in% ly]

plt1_classic = plt1_bb[plt1_bb$ProductNo. %in% classic,]
plt1_classic$new = "classic"
ttst2 = plt1_classic[plt1_classic$year == 'this year', ]

plt1_classic= plt1_classic[plt1_classic$ProductNo. %in% 
               (plt1_classic %>% 
  arrange(desc(sales)) %>% head(10))$ProductNo., ]

plt1_new = plt1_bb[!plt1_bb$ProductNo. %in% classic,]
plt1_new$new = "new"
ttst22 = plt1_new
plt1_new = plt1_new %>% arrange(desc(sales)) %>% head(10)

# 
# plt1_bb = rbind(plt1_classic, plt1_new)
 
plot_ly(data = plt1_classic, x = ~ProductNo., y = ~inventory, z = ~sales,
        type = 'scatter3d', 
        color = ~year,
        # symbol = "diamond",
        colors = viridis(45,alpha = .6),
        mode = 'markers',
        marker = list(size = ~ log(sales), opacity = .7)) %>%
  add_trace(data = plt1_new, x = ~ProductNo., y = ~inventory, z = ~sales,
            type = 'scatter3d', 
        color = ~new,
        # symbol = C,
        colors = viridis(45,alpha = .6),
        mode = 'markers',
        marker = list(size = ~ log(sales), opacity = .7, symbol = "diamond")
        # symbol = list("square")
        ) %>% 
  layout(showlegend = FALSE, 
         title ="sales&inventory on SKU")
 
```

Row {.tabset-fade data-heights=325 .colored }
-----------------------------------------------------------------------

### cor

```{r, echo = F}
# df_q12
cor = df_q12[6:dim(df_q12)[2]] %>%cor()%>% data.frame()
m = cor %>% as.matrix()
x = cor %>% names() 
# matrix(rnorm(9), nrow = 3, ncol = 3)
fig <- plot_ly(x = x, y = x, 
    z = m, type = "heatmap", colors= viridis::plasma(16,.1,.3)
) %>% layout(title = "correlations")

fig
```

### test

```{r, echo = F}
# library(car)
# ?linearHypothesis()
ttst = rbind(plt1_cl_ttest, plt1_new_ttest)
t.test(sales ~ new, data = ttst )
print("the new stores showed insignificant difference in sales compare to old stores")
# 
# ttest2 = rbind(ttst2, ttst22)
# t.test(sales ~ new, data = ttest2 )
# print("the new stores showed insignificant difference in sales compare to old stores")

```

---

Column {.tabset .tabset-fade data-heights=625 data-width=375 .colored }
-----------------------------------------------------------------------

### below used data from first sheet in Q1, look detailly on specific time span comparison
      17 appears to have better sales / transaction / traffic data than 16
 

Column {.tabset .tabset-fade data-heights=625 data-width=625 .colored }
-----------------------------------------------------------------------

### traffic comparison 16~17

```{r, echo = F}

highchart() %>% 
    hc_add_series(plt2, 
                  hcaes(x = as.character(date), 
                        y = traffic,
                        group = year, 
                        color = year), type = "line") %>%  # # series.name and series.color 
  hc_tooltip(crosshairs = TRUE, borderWidth = 1.5,pointFormat = 
                paste(
                  "storetype: <b>{series.name}<b> <br> traffic: <b>{point.y:.2f}<b>" 
                 )) %>%  hc_title(text = "traffic comparison 16~17") 


# df11 %>% head()
# paste0((plt1 %>% names())[4:7][1])
```

### transaction comparison 16~17

```{r,echo = F}
# transaction), sales_amt = sum(sales_amt), sold_unit = sum(sold_unit))
highchart() %>% 
    hc_add_series(plt2, 
                  hcaes(x = as.character(date), 
                        y = transaction,
                        group = year, 
                        color = year), type = "line") %>%  # # series.name and series.color 
  hc_tooltip(crosshairs = TRUE, borderWidth = 1.5,pointFormat = 
                paste(
                  "storetype: <b>{series.name}<b> <br> transaction: <b>{point.y:.2f}<b>" 
                 ))   %>%  hc_title(text = "transaction comparison 16~17") 

```

### sales_amt comparison 16~17

```{r,echo = F}
# transaction), sales_amt = sum(sales_amt), sold_unit = sum(sold_unit))
highchart() %>% 
    hc_add_series(plt2, 
                  hcaes(x = as.character(date), 
                        y = sales_amt,
                        group = year, 
                        color = year), type = "line") %>%  # # series.name and series.color 
  hc_tooltip(crosshairs = TRUE, borderWidth = 1.5,pointFormat = 
                paste(
                  "storetype: <b>{series.name}<b> <br> sales_amt: <b>{point.y:.2f}<b>" 
                 ))  %>%  hc_title(text = "sales_amt comparison 16~17") 

```


### sold_unit comparison 16~17

```{r,echo = F}
# transaction), sales_amt = sum(sales_amt), sold_unit = sum(sold_unit))
highchart() %>% 
    hc_add_series(plt2, 
                  hcaes(x = as.character(date), 
                        y = sold_unit,
                        group = year, 
                        color = year), type = "line") %>%  # # series.name and series.color 
  hc_tooltip(crosshairs = TRUE, borderWidth = 1.5,pointFormat = 
                paste(
                  "storetype: <b>{series.name}<b> <br> sold_unit: <b>{point.y:.2f}<b>" 
                 ))  %>%  hc_title(text = "sold_unit comparison 16~17") 

```

Row {data-heights=700 data-width=625 .no-padding .colored}
-------------------------------------

```{r, echo = F}
 
fig <- plot_ly()
 

for (i in 1:4){
 
    pp = plt1[plt1$year == '2016',] %>% select((plt1 %>% names())[4:7][i])
    names(pp) = c("store_type", 'date', 'value')
    fig = fig %>% 
          add_pie(data =  pp, 
              labels = ~store_type, 
              values = ~value,
              hole = .4,
              textinfo = 'label+percent',
              textposition = 'inside',
              # hoverinfo = 'text',
              # text = ~paste0(bms_industry, sum_bill_amount),
              name = paste0("2016",(plt1 %>% names())[4:7][i]) ,
              domain = list(row = 0, column = i-1),
              marker = list(colors = 
                              inferno(8, begin  = .2, end = .8,
                                      direction = -1),
                          line = list(color = '#FFFFFF', width = 1)),
            showlegend = T) %>% layout(title= paste0((plt1 %>% names())[4:7][i]))
    i = i+1
   
}

for (i in 1:4){

   
    pp = plt1[plt1$year == '2017',] %>% select((plt1 %>% names())[4:7][i])
    names(pp) = c("store_type", 'date', 'value')
    fig = fig %>% 
          add_pie(data =  pp, 
              labels = ~store_type, 
              values = ~value,
              hole = .4,
              textinfo = 'label+percent',
              textposition = 'inside',
              # hoverinfo = 'text',
              # text = ~paste0(bms_industry, sum_bill_amount),
              name =  paste0("2017",(plt1 %>% names())[4:7][i]) ,
              domain = list(row = 1, column = i-1),
              marker = list(colors = 
                              inferno(8, begin  = .2, end = .8,
                                      direction = -1),
                          line = list(color = '#FFFFFF', width = 1)),
            showlegend = T) %>% layout(title= paste0((plt1 %>% names())[4:7][i]))
    i = i+1

}
 
fig <- fig %>% layout(title = "16&17 key value comparison",
                      showlegend = F,
                      grid=list(rows=2, columns=4),
                      xaxis = list(
                        showgrid = FALSE, 
                        zeroline = FALSE, 
                        showticklabels = FALSE),
                      yaxis = list(
                        showgrid = FALSE, 
                        zeroline = FALSE, 
                        showticklabels = FALSE))

fig
```

### insight
 
comparing to 2016 (4 pie charts on the upper part), roughly speaking that `sport_performance` business has been replaced by `flagship` as largest business in 2017 (4 pie charts on the lower part) , in this dataset.




Question 2 predictions
=======================================================================

### this part used fbprophet

```{r}

df2 = readxl::read_excel("Question 2.xlsx", sheet = 1)
# library(prophet)
# m <- prophet(holidays = holidays)
# m <- add_country_holidays(m, country_name = 'US')
# m <- fit.prophet(m, df)

```

