---
title: "nike_report3"
author: "Siming Yan"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    # css: bootstrap.min.css
    theme: yeti
---

<style>
.colored {
  background-color: #FAFAFA;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r setup2, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(reshape2)
# library(lubridate)
# library(highcharter) # Interactive data visualizations
library(viridis)
library(DT)
library(lfe)
library(stargazer) 
library(stringr) 
library(zoo)   
library(plotly)
# reticulate::use_condaenv("siming")
# vignette("highcharter")
# vignette("highcharts-api")
```


```{r, include=FALSE}
# Create a custom theme for the plots. 
kbt <- function(...){
  knitr::kable(..., format.args = list(big.mark = ',', scientific = F)) %>%
    kableExtra::kable_styling(c("striped", "condensed"),
                               full_width = F,
                               position = "center",
                               row_label_position = "c") %>%
   row_spec(0, bold = T)
}

stg <- function(...){
  stargazer::stargazer(..., 
          type = "text",
          # style = "qje",
          # title = "daily_kwh ~ post:encouraged|customer_id + no.bill|0|customer_id",
          keep.stat = c("n", "ser"),
          digits = 5)
}

parent_cat1 = c("#6A040F","#9D0208","#E04A46","#DC2F02","#E85D04","#F48C06","#faa307","#f3e194")
```

Question 3 causal inferences 
=======================================================================


Row {data-heights=700 data-width=125 .no-padding .colored}
-------------------------------------
 
### data walkthrough

```{r, include = F}

df31 = readxl::read_excel("Question3.xlsx", sheet = 1) 
df32 = readxl::read_excel("Question3.xlsx", sheet = 2, skip = 3, col_names = F)
```

```{r, echo=F}
cnt31 = apply(df31, 2, function(x) length(unique(x))) %>% data.frame()
names(cnt31) = 'count_distinct'
dropcol = rownames(cnt31)[which(cnt31$count_distinct == 1)]
df31 = df31 %>% select(-dropcol)
datatable(cnt31)
```


Row {data-heights=1000 data-width=1000 .no-padding .colored}
-------------------------------------

### correlation plot
```{r, echo = F, warning=F, message=F, echo = F}
# df31
library(data.table)
cor = df31[!df31 %>% names() %like% "COLOR"]
cor = cor[,2:dim(cor)[2]] %>%cor()%>% data.frame()
m = cor %>% as.matrix()
x = cor %>% names() 
# matrix(rnorm(9), nrow = 3, ncol = 3)
fig <- plot_ly(x = x, y = x, 
    z = m, type = "heatmap", colors= viridis::plasma(16,.1,.3)
) %>% layout(title = "correlations")
fig
```


Row {data-heights=700 data-width=625 .no-padding .colored}
-------------------------------------

### regressions

```{r, warning = F, message = F, results='asis', echo=F}
# df31 %>% group_by()
# df31
fixed_eff = df31[df31 %>% names() %like% "IF"] %>% names()
fixed_eff = fixed_eff %>% append(c("COLOR_CD_1", "COLOR_CD_2", "COLOR_CD_3"))
paras = df31[!df31 %>% names() %in% fixed_eff] %>% names()
paras = paras[3:length(paras)]

para_str = paste(paras, collapse="+")
fe_str =  paste(fixed_eff, collapse="+") 
fml1 = as.formula(paste("SALES_QTY~", para_str,
                        "-1-SSNRK_1ST_SKU_LAUNCH-NUM_COLOR_DESC -LAST_SEASON_INDICATOR",
                        "|", fe_str
                        ))
reg1 = felm(fml1, data = df31) 
print(fml1)
print(
  "
  "
)
stargazer(reg1, type = "html")
```

### memos

this is a fixed effect model by using felm function from car package, the categorical variables are suppressed in fixed-effects, they are considered but not included in the output report, the formula has shown above, three parameters are eliminated due to vacancy in value caused by `Multicollinearity`.

the significant variables including:

`SEASON_SINCE_1ST_SKU_LAUNCH` which means Number of seasons since the SKU was launched, 10 more sales for an extra season. 


`NUMSKU_SAME_STYLE_IN1SSN` Number of products with the same style, popular styles can be more welcomed in our market. `NUMSKU_SAME_PF_IN1SSN` (Number of products with the same power franchise) also statistically significant. however `NUMSKU_SAME_MODEL_IN1SSN` not significant, which implys model is not a key role in this dataset.


`OMD_DAYS_SINCE_SEASON_BEGIN` Number of days since SKU launch in the season, has a negative value and statistically significant. which means in a season, the SKU can become more unpopular from day to day.



Row {data-heights=700 data-width=625 .no-padding .colored}
-------------------------------------

### rough regression on categorical variables

```{r, echo = F, warning = F, results='asis'}
para_str
df31[paras]
library(lme4)
fe_str
fm2 = as.formula(paste("SALES_QTY~0+",fe_str))
reg2 = felm(fm2, data = df31) 
print(fm2)
stargazer(reg2, type = "html")
```



### memos

categorical variables only regression, the formula has shown above, parameters are eliminated due to vacancy in value caused by `Multicollinearity`.

significant variables are:

`IF_GENERAL_PRICE`
`IF_TRIPLEWHITE`
`IF_SEASONAL_SILO_SU`                                             
`IF_NEW_SEASONAL`

which indicates that: 
basically customers are focusing on two things: the price and if the sku is new. there are two more colors go significant, but the potential color ~ price relation is not clear.